% Memo: Executive Brief for DWTS Programming Leadership

\newpage
\thispagestyle{empty}

\begin{center}
\Large\textbf{AUDIT MEMORANDUM}
\end{center}

\vspace{0.5em}
\noindent\rule{\textwidth}{1.5pt}
\vspace{0.3em}

\begin{tabular}{@{}ll}
\textbf{TO:}      & Executive Producer, \emph{Dancing with the Stars} \\
\textbf{FROM:}    & Team \#2617892 --- Modeling \& Audit Unit \\
\textbf{DATE:}    & January 30, 2026 \\
\textbf{SUBJECT:} & \textbf{Rule Audit \& Dynamic Mechanism Recommendation}
\end{tabular}

\vspace{0.3em}
\noindent\rule{\textwidth}{1.5pt}
\vspace{0.8em}

\subsection*{Executive Summary}

We audited DWTS eliminations across 34 seasons using a rule-consistent inversion engine and Bayesian posterior reconstruction. The core question: \textbf{Can published rules explain observed eliminations without observing fan votes'}

\textbf{Answer: yes.} All seasons are feasible under the published rules (no positive slack $S^*$). However, feasibility does not imply certainty: several weeks remain weakly identified, and wide posterior intervals persist.

\subsection*{Three Principal Findings}

\begin{enumerate}[itemsep=0.2em]
    \item \textbf{Rule Transparency Holds.} \newline
    The optimization audit finds $S^*=0$ across seasons, indicating the rules are sufficient to explain eliminations under our model assumptions.
    
    \item \textbf{Structural Uncertainty Persists.} \newline
    Even with rule consistency, some weeks exhibit wide posterior HDIs (e.g., max width \(\approx 0.46\) in the Bobby Bones case), revealing underidentification in the 50/50 system.
    
    \item \textbf{Counterfactual Stability.} \newline
    Mean Kendall's Tau is \(\approx 0.455\) and reversal rate is \(\approx 0.174\). A dynamic schedule preserves these fairness signals while improving audience influence.
\end{enumerate}

\subsection*{Recommendation: Dynamic Adaptive Weighting}

We recommend a dynamic rule that shifts from judge-heavy to fan-heavy weighting:

\begin{itemize}[itemsep=0.1em]
    \item \textbf{Early weeks (1--5):} emphasize judges (\(\alpha \approx 0.7\)) for skill screening.
    \item \textbf{Late weeks:} gradually shift to fans (\(\alpha \to 0.4\)) for engagement.
    \item \textbf{Static fallback:} 60/40 remains a stable baseline point on the Pareto frontier.
\end{itemize}

\subsection*{Scope \& Limitations}

\begin{itemize}[itemsep=0.1em]
    \item Fan votes are unobserved; we infer feasible posteriors, not exact values.
    \item Counterfactuals assume fan behavior is invariant to rule changes.
\end{itemize}

\vspace{0.8em}
\hfill\textbf{--- Team \#2617892, Modeling \& Audit Unit}

\vspace{0.3em}
\hfill\textit{Full technical methodology in attached report.}
