% Section 9: Conclusions and Recommendations
% 缁撹涓庡缓璁?

\section{Conclusions}
\label{sec:conclusion}

\subsection{Summary of Findings}

This paper developed a comprehensive framework for inferring fan votes from \emph{Dancing with the Stars} elimination data. Our key findings:

\begin{enumerate}[itemsep=0.2em]
    \item \textbf{Dual-Core Inversion:} Successfully reconstructed fan vote distributions for 32 of 34 seasons using hybrid LP/MILP with 100\% constraint satisfaction and median bound width of 8.3\%.
    
    \item \textbf{Model-Data Mismatch Detection:} Identified S32/S33 with constraint slack $S^* > 0$, revealing mathematical complexity introduced by Judges' Save mechanics. This is \emph{not} evidence of manipulation, but highlights modeling challenges in S28+ rules.
    
    \item \textbf{Professional Dancer Effect:} Survival analysis reveals professional partner as the dominant predictor (likelihood ratio test $\chi^2 = 47.3$, $p < 0.001$; C-index improvement $\Delta C = 0.09$)---larger effect than celebrity type or prior fame.
    
    \item \textbf{Weighted Percent System:} Proposed mechanism ($0.6J^\% + 0.4V$) reduces definite-wrongful eliminations from \textbf{40 to 3} under interval-robust classification.
\end{enumerate}

\subsection{Recommendations}

\begin{enumerate}[itemsep=0.2em]
    \item \textbf{Pre-Broadcast Transparency:} Run LP/MILP solver before broadcast; flag episodes with $S^* > 0.5$ for producer review.
    \item \textbf{Adopt Weighted Percent:} $\text{Score}_i = 0.6 \cdot J_i^\% + 0.4 \cdot V_i$ --- transparent ``60\% skill, 40\% popularity.''
    \item \textbf{Judges' Save Transparency:} Document criteria for judge save decisions to reduce model-data mismatches.
\end{enumerate}

\subsection{Limitations}

\begin{itemize}[itemsep=0.1em]
    \item Unobserved heterogeneity (social media campaigns, news events).
    \item Weaker bounds for rank-only seasons (S28--S34).
    \item Cannot determine mismatch \emph{cause} (only detection).
    \item Counterfactual assumes unchanged voting behavior.
\end{itemize}

\subsection{Future Work}

Future extensions: (1) real-time dashboard for producers, (2) international expansion to \emph{Strictly Come Dancing} and other franchises, (3) incorporating social media sentiment to tighten bounds.

\vspace{0.5em}
\noindent\textbf{Key Takeaway:} The current DWTS system produces 40 definite-wrongful eliminations across 230 rounds (17.4\%). Our Weighted Percent System reduces this to 3 (1.3\%)---a robust improvement verified by interval-based classification that accounts for fan vote estimation uncertainty.
